### 2022-10-01 ersteops/templates/printpdf/paperless_template.tex
remove no need content

    {% for item in content.json_medications_farma %}
      {% if forloop.counter0 == 0 %}
        \put(0.26321649,0.32734768){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
        \put(0.30511372,0.32734768){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
        \put(0.33483843,0.32720095){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_hrs }}\end{tabular}}}}%
      {% endif %}
      {% if forloop.counter0 == 1 %}
        \put(0.26342897,0.31837723){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
        \put(0.3053262,0.31837723){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
        \put(0.33505092,0.31823051){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_hrs }}\end{tabular}}}}%
      {% endif %}
      {% if forloop.counter0 == 2 %}
        \put(0.26308947,0.3081286){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
        \put(0.3049867,0.3081286){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
        \put(0.33471142,0.30798187){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_hrs }}\end{tabular}}}}%
      {% endif %}
    {% endfor %}

    {% for item in content.json_medications_amina %}
      {% if forloop.counter0 == 0 %}
        \put(0.26517407,0.28858281){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
        \put(0.30543707,0.28852296){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
        \put(0.33395328,0.28858473){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_hrs }}\end{tabular}}}}%
      {% endif %}
      {% if forloop.counter0 == 1 %}
        \put(0.26491781,0.27987623){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
        \put(0.30518081,0.27981639){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
        \put(0.33369702,0.27987816){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_hrs }}\end{tabular}}}}%
      {% endif %}
      {% if forloop.counter0 == 2 %}
        \put(0.26516689,0.27001966){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
        \put(0.3054299,0.26995982){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
        \put(0.3339461,0.27002158){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_hrs }}\end{tabular}}}}%
      {% endif %}
    {% endfor %}

    {{ content.medications }}

>>>>

    {% for item in content.json_medications_farma %}
      {% if forloop.counter0 == 0 %}
        \put(0.26321649,0.32734768){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_name }}\end{tabular}}}}%
        \put(0.30511372,0.32734768){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_dose }}\end{tabular}}}}%
        \put(0.33483843,0.32720095){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_hrs }}\end{tabular}}}}%
      {% endif %}
      {% if forloop.counter0 == 1 %}
        \put(0.26342897,0.31837723){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_name }}\end{tabular}}}}%
        \put(0.3053262,0.31837723){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_dose }}\end{tabular}}}}%
        \put(0.33505092,0.31823051){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_hrs }}\end{tabular}}}}%
      {% endif %}
      {% if forloop.counter0 == 2 %}
        \put(0.26308947,0.3081286){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_name }}\end{tabular}}}}%
        \put(0.3049867,0.3081286){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_dose }}\end{tabular}}}}%
        \put(0.33471142,0.30798187){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_hrs }}\end{tabular}}}}%
      {% endif %}
    {% endfor %}

    {% for item in content.json_medications_amina %}
      {% if forloop.counter0 == 0 %}
        \put(0.26517407,0.28858281){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_name }}\end{tabular}}}}%
        \put(0.30543707,0.28852296){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_dose }}\end{tabular}}}}%
        \put(0.33395328,0.28858473){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_hrs }}\end{tabular}}}}%
      {% endif %}
      {% if forloop.counter0 == 1 %}
        \put(0.26491781,0.27987623){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_name }}\end{tabular}}}}%
        \put(0.30518081,0.27981639){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_dose }}\end{tabular}}}}%
        \put(0.33369702,0.27987816){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_hrs }}\end{tabular}}}}%
      {% endif %}
      {% if forloop.counter0 == 2 %}
        \put(0.26516689,0.27001966){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_name }}\end{tabular}}}}%
        \put(0.3054299,0.26995982){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_dose }}\end{tabular}}}}%
        \put(0.3339461,0.27002158){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_hrs }}\end{tabular}}}}%
      {% endif %}
    {% endfor %}

### 2022-10-01 ersteops/templates/printpdf/rendered_template.tex
update medications

    %Folio
    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 72\end{tabular}}}}%

@@

    %Paciente
    \put(0.08748365,0.54597578){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize F55 - Lillia Sanchez Jaime\end{tabular}}}}%
    \put(0.32347436,0.544854){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 5556782349\end{tabular}}}}%
    \put(0.05306258,0.51467754){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Masculino\end{tabular}}}}%
    \put(0.12394486,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 15\end{tabular}}}}%
    \put(0.11025071,0.53602224){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Lillia Sanchez Jaime\end{tabular}}}}%
    \put(0.11717691,0.52661865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%

@@

    %Medicamentos (to_fix)
    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont [\{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Hemoderivado-Solucion\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 120\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 1\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} , \{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Hemoderivado-Hemoderivado\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 120\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 2\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} , \{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Hemoderivado-Hemoderivado\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 123\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 3\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} , \{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Cardiovascular-Desfibrilacion\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 124\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 4\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} , \{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Cardiovascular-Cardioversion\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 125\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 5\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} ]\end{tabular}}}}%
    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont la medi\end{tabular}}}}%
    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Hemoderivado-Solucion - 120 - 0 hrs\\Hemoderivado-Hemoderivado - 120 - 0 hrs\\Hemoderivado-Hemoderivado - 123 - 0 hrs\\Cardiovascular-Desfibrilacion - 124 - 0 hrs\\Cardiovascular-Cardioversion - 125 - 0 hrs\\\end{tabular}}}}%

          \put(0.04964403,0.32745002){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 120\end{tabular}}}}%
          \put(0.11108429,0.32756971){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 1\end{tabular}}}}%

    [\{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Hemoderivado-Solucion\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 120\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 1\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} , \{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Hemoderivado-Hemoderivado\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 120\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 2\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} , \{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Hemoderivado-Hemoderivado\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 123\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 3\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} , \{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Cardiovascular-Desfibrilacion\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 124\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 4\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} , \{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Cardiovascular-Cardioversion\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 125\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 5\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} ]

@@

    %Finalizacion
    \put(0.56613143,0.28790386){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%\
    \put(0.59939617,0.27975509){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
    \put(0.61896758,0.26988471){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize patitas\end{tabular}}}}%
    \put(0.59042647,0.26068666){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize dasdasd\end{tabular}}}}%
    \put(0.53599859,0.25148177){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize sin tum\end{tabular}}}}%
    \put(0.81652804,0.25194696){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize el faisan\end{tabular}}}}%

>>>>

    %Folio
    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 76\end{tabular}}}}%

@@

    %Paciente
    \put(0.08748365,0.54597578){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize F55 - Lillia Sanchez Jaime\end{tabular}}}}%
    \put(0.32347436,0.544854){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 5556782349\end{tabular}}}}%
    \put(0.05306258,0.51467754){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Masculino\end{tabular}}}}%
    \put(0.12394486,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 12\end{tabular}}}}%
    \put(0.11025071,0.53602224){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Lillia Sanchez Jaime\end{tabular}}}}%
    \put(0.11717691,0.52661865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%

@@

    %Medicamentos (to_fix)
    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont []\end{tabular}}}}%
    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont la medi\end{tabular}}}}%
    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont \end{tabular}}}}%

@@

    %Finalizacion
    \put(0.56613143,0.28790386){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%\
    \put(0.59939617,0.27975509){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
    \put(0.61896758,0.26988471){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize patitas\end{tabular}}}}%
    \put(0.59042647,0.26068666){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize dasdasd\end{tabular}}}}%
    \put(0.53599859,0.25148177){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Con Tum\end{tabular}}}}%
    \put(0.81652804,0.25194696){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize el faisan\end{tabular}}}}%

      \put(0.79939617,0.25975509){\includegraphics[scale=0.3]{signature_medic}}%
      %\put(0.78960956,0.44450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Firma Médico\end{tabular}}}}%

    \put(0.58960956,0.11450476){\includegraphics[scale=0.5]{client_signature}}%
    \put(0.64203741,0.04450476){\includegraphics[scale=0.5]{client_signature}}%
    %\put((0.64203741,0.06450476){\includegraphics[scale=0.5]{client_signature}}%
    \put(.64090291,0.20857036){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
    %\put(0.64203741,0.06450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
